<!--
$Header: /cvsroot/marf/marf/doc/src/tex/notation.tex,v 1.1 2002/12/14 02:57:52 mokhov Exp $
-->

<sect1 id="notation">
 <title>Terminology and Notation</title>

 <para>
  The term <quote>MARF</quote> will be
  to refer to the software that accompanies this
  documentation.
 </para>

 <para>
  An <firstterm>application programmer</firstterm>
  could be anyone who is using, or wants to use, any part of the
  <productname>MARF</productname> system.
  A <firstterm>MARF developer</firstterm>
  is a core member of MARF who is hacking away the
  <productname>MARF</productname> system.

 </para>

 <para>
  We use <filename>/usr/local/pgsql/</filename> as the root
  directory of the installation and <filename>/usr/local/pgsql/data</filename>
  as the directory with the database files.  These directories may vary
  on your site, details can be derived in the <citetitle>Administrator's Guide</citetitle>.
 </para>

 <para>
  In a command synopsis, brackets
  (<literal>[</literal> and <literal>]</literal>) indicate an optional phrase or keyword.
  Anything in braces
  (<literal>{</literal> and <literal>}</literal>) and containing vertical bars
  (<literal>|</literal>)
  indicates that you must choose one alternative.
 </para>

 <para>
  Examples will show commands executed from various accounts and programs.
  Commands executed from a Unix shell may be preceded with a dollar sign
  (<quote><literal>$</literal></quote>).  Commands executed from particular user
  accounts such as <systemitem>root</> or <systemitem>postgres</> are specially flagged and explained.
  <acronym>SQL</acronym> commands may be preceded with
  <quote><literal>=&gt;</literal></quote>
  or will have no leading prompt, depending on the context.
 </para>

 <note>
  <para>
   The notation for
   flagging commands is not universally consistent throughout the
   documentation set.
   Please report problems to
   <email></email>.
  </para>
 </note>

</sect1>

<!-- Keep this comment at the end of the file
Local variables:
mode:sgml
sgml-omittag:nil
sgml-shorttag:t
sgml-minimize-attributes:nil
sgml-always-quote-attributes:t
sgml-indent-step:1
sgml-indent-data:t
sgml-parent-document:nil
sgml-default-dtd-file:"./reference.ced"
sgml-exposed-tags:nil
sgml-local-catalogs:("/usr/lib/sgml/catalog")
sgml-local-ecat-files:nil
End:
-->
